### 2022-09-26 manuscript/manuscript.tex
ms notes

\documentclass[11pt]{article}
\RequirePackage{fullpage}
\RequirePackage[font=small,labelfont=bf]{caption}
\RequirePackage{amsmath,amssymb,amsthm}
\RequirePackage{graphicx}
\RequirePackage[hidelinks]{hyperref}
\RequirePackage{subcaption}
\RequirePackage{wasysym}
\RequirePackage{authblk}
\RequirePackage{bm}
\RequirePackage{bbm}
% \RequirePackage[osf]{mathpazo}
\RequirePackage[bibstyle=authoryear,citestyle=authoryear-comp,maxbibnames=9,maxcitenames=1,backend=biber,natbib=true,uniquelist=false,hyperref=true]{biblatex}
\usepackage{color}
\usepackage{nicefrac}

@@

@@

As $s \to 0$, the fitness distribution, put on a scale reflecting the fitness
relative at one moment in time, travels leftwards and changes shape. It has
been difficult to find dynamic equations for the rate of the ratchet, since
lower moments of the distribution, such as the variation, depend on higher
moments, such as the skew \parencite{Good2013-lp,Haigh1978-gt,Higgs1995-xc}.
This moment closure problem occurs regardless of whether one models the count
number of deleterious mutations (XXX) or the fitness distribution (XXX).

We can approximate the mapping between the distribution of deleterious
mutations in the population, and the fitness distribution.

Assuming $s$ is small, we can write express this in terms of the additive
genetic variance,

\begin{align}
  V(f) \approx s^2 \V(n) + \delta_\text{LD}.
\end{align}

@@

\begin{align}

\end{align}

- We need to mention the two heterozygosities (S&C '16 says they diverge under
$N_e s < 1$ -- could explain anything we see?)

>>>>

\documentclass[11pt]{article}
\RequirePackage{fullpage}
\RequirePackage[font=small,labelfont=bf]{caption}
\RequirePackage{amsmath,amssymb,amsthm}
\RequirePackage{graphicx}
\RequirePackage[hidelinks]{hyperref}
\RequirePackage{subcaption}
\RequirePackage{wasysym}
\RequirePackage{authblk}
\RequirePackage{bm}
% \RequirePackage{bbm}
\RequirePackage[osf]{mathpazo}
\RequirePackage[bibstyle=authoryear,citestyle=authoryear-comp,maxbibnames=9,maxcitenames=1,backend=biber,natbib=true,uniquelist=false,hyperref=true]{biblatex}
\usepackage{color}
\usepackage{nicefrac}

@@

\subsection*{Effective Population Size for Pairwise Diversity}

When quantifying genetic variation with average pairwise diversity, often a
single effective population size parameterizes the rate of pairwise
coalescences of the entire evolutionary history. This is sufficient for
constant-rate Kingman coalescences, but weak selection distorts genealogies
(desai and nicolaison), creating a coalescent process with non-constant rates.
Consequently, the expected pairwise coalescent time between two lineages $i$
and $j$

\begin{align}
  \E(T) &= \sum_i T(i) \P(\mathrm{MRCA}(i)) \\
        &= \sum_i T(i) \prod_{t=1}^i \left(1 - \frac{1}{2N_{e(i)}}\right)
\end{align}

% ADD TO INTRO TODO
Comment about characteristic scale $\nicefrac{\mu}{s}$. Is the fact that we see
BGS on megabase scales because this is the only scale we can detect strong
selection under?

approximately $\pi \approx 4N_e \mu$ (for low mutation rate). However, this
assumes a constant Kingman coalescent with coalescent effective population size
$N_e$.

\subsection*{}

@@

As $s \to 0$, the fitness distribution, put on a scale reflecting the fitness
relative at one moment in time, travels leftwards and changes shape. It has
been difficult to find dynamic equations for the rate of the ratchet and
fitness distribution, since lower moments of the distribution, such as the
variation, depend on higher moments, such as the skew
\parencite{Good2013-lp,Haigh1978-gt,Higgs1995-xc}. This is known as the ``moment
closure problem" and it occurs regardless of whether one models the count
number of deleterious mutations (XXX) or the fitness distribution (XXX).

We can approximate the mapping between the distribution of deleterious
mutations in the population, and the fitness distribution. It is worth noting
that the count of deleterious mutations in an individual $i$ can be written
$n_i = \sum_l^{L} g_l$ where each $g_l$ is an indicator variable for whether
the individual carries a mutation at position $l$. Then, $\V_i(n) = \sum_l
\V(g_l) + \sum_{i,j}\cov(g_i, g_j)$.

the
number of deleterious mutations in gamete $i$; thus $V(n) = \sum_i^{2N} V(x_i)
+ \sum_{i \ne j} \cov(x_i, x_j)$ where the last term is the correlation among
gamete mutation counts, which is an LD quantity. Then, assuming $s$ is small,
we can write express this in terms of the additive genetic variance,

\begin{align}
  V(f) &\approx s^2 \V_a(n) + \delta_\text{LD}
\end{align}

@@

Throughout, it's worthwhile to keep into mind many population-level
macro-states are simply distributional summaries of the current population. For
example, the variance in deleterious mutations in the population is simply,
$\V(n) = \nicefrac{1}{2N} \sum_i (x_i - \mu_x)^2$

- We need to mention the two heterozygosities (S\&C '16 says they diverge under
$N_e s < 1$ -- could explain anything we see?)
